---
title: "Data Discovery Tool, Start Up"
output: html_notebook
---
2017-09-21

The Data Discovery Tool (ddt) created by USEPA for use with Water Quality Data Portal (v1.1.0.0000).  The modified version with QAQC is version 1.1.3.0000.

# Start Up
The base version of the ddt ships as a self contained program.

The QAQC modifications are included in a zip file with all the necessary parts to run the ddt as a stand alone application in R.  

Before running the code you will need to change the working directory to where the ddt files are located.  In R, from the menu bar choose "File", "Change Dir", then select the location of the ddt files. 

Then use the code below in R to start the ddt.  Just copy and paste into the R console.

```{r, eval=FALSE}
# Run the app
require(shiny)
runApp(launch.browser = T)
```

If you know the directory of the ddt files you can add this information to the code (see below).
```{r, eval=FALSE}
# Change Directory
myDir <- file.path("C:","Users","Erik.Leppo","OneDrive - Tetra Tech, Inc"
                ,"MyDocs_OneDrive","GitHub","DataDiscoveryTool")
setwd(myDir)
# Run the app
require(shiny)
runApp(launch.browser = T)

```

Alternatively, if you have RStudio you can open either server.R or ui.R then click the "Run App" button.