---
title: "Data Discovery Tool, Packages"
output: html_notebook
---
2017-08-14

The Data Discovery Tool (ddt) created by USEPA for use with Water Quality Data Portal (v1.1.0.0000).

# Packages
A number of packages are included with the ddt and ship in the R portal version.

In order run as a stand alone version the user will need the to install multiple packages as noted in the R code below.

The only "new" package added for the QAQC work by Tetra Tech is "XLConnect".
```{r, eval=FALSE}
# libraries to be installed
data.packages = c("assertthat"
                  , "base64enc"
                  , "chron"
                  , "data.table"
                  , "dataRetrieval"
                  , "DBI"
                  , "devtools"
                  , "dplyr"
                  , "DT"
                  , "ggplot2"
                  , "git2r"
                  , "htmlwidgets"
                  , "httpuv"
                  , "httr"
                  , "jsonlite"
                  , "lazyeval"
                  , "leaflet"
                  , "lubridate"
                  , "memoise"
                  , "openssl"
                  , "png"
                  , "R6"
                  , "raster"
                  #, "rCharts" #non-CRANN
                  , "readr"
                  , "rstudioapi"
                  , "scales"
                  , "shiny"
                  , "shinyBS"
                  , "sourcetools"
                  , "sp"
                  , "stringr"
                  , "tibble"
                  , "whisker"
                  , "withr"
                  , "xml2"
                  , "xtable"
                  , "XLConnect"
                  )
# install via lapply
lapply(data.packages,function(x) install.packages(x))
```

One package, rCharts, is a non-CRANN package and needs to be installed separately.
```{r, eval=FALSE}
# Install non-CRANN packages
require(devtools)
install_github("ramnathv/rCharts")

```

If after running the ddt the user is presented with an error message about not having a package then the user should reinstall that specific package.
```{r, eval=FALSE}
# libraries to be installed
data.packages = c("MissingPackage")
# install via lapply
lapply(data.packages,function(x) install.packages(x))
```

