---
title: "Editable Table"
output: html_notebook
---

Data Discovery Tool (ddt) v1.1.1.9002 (working).

Attempt to create an editable table of the QAQC Decision file (knowledge base).

* Copy the accompanying file (DDT_QAQC_Default.xlsx) to your working directory.

* Will need to use "devtools" to get from GitHub a special version of "DT" (see code below).

```{r, eval=FALSE}
devtools::install_github('rstudio/DT@feature/editor')
```

# Example

https://github.com/rstudio/DT/issues/28


https://yihui.shinyapps.io/DT-proxy/


### formatting
https://rstudio.github.io/DT/010-style.html

# original
```{r, eval=FALSE}
library(shiny)
library(DT)

shinyApp(
  ui = fluidPage(
    DT::dataTableOutput('x1')
  ),
  server = function(input, output, session) {
    x = iris
    x$Date = Sys.time() + seq_len(nrow(x))
    output$x1 = DT::renderDataTable(x, selection = 'none')

    proxy = dataTableProxy('x1')

    observeEvent(input$x1_cell_edit, {
      info = input$x1_cell_edit
      str(info)
      i = info$row
      j = info$col
      v = info$value
      x[i, j] <<- DT:::coerceValue(v, x[i, j])
      replaceData(proxy, x, resetPaging = FALSE)
    })
  }
)
```


# slightly modified
```{r, eval=FALSE}
#devtools::install_github('rstudio/DT@feature/editor')
# above version of DT required for table editing

library(shiny)
library(DT)

shinyApp(
  ui = fluidPage(
    DT::dataTableOutput('x1')
  ),
  server = function(input, output, session) {
    
    x = iris
    x$Date = Sys.time() + seq_len(nrow(x))
    
    output$x1 = DT::renderDataTable(x, rownames = FALSE, selection='none')
    
    proxy = dataTableProxy('x1')
    
    observeEvent(input$x1_cell_edit, {
      info = input$x1_cell_edit
      str(info)
      i = info$row
      j = info$col + 1
      v = info$value
      x[i, j] <<- DT:::coerceValue(v, x[i, j])
      replaceData(proxy, x, resetPaging = FALSE, rownames = FALSE)
    })
  }
)
```

# Working Example with Knowledge Base

Only allows True or False in "apply" column.

```{r, eval=FALSE}
#devtools::install_github('rstudio/DT@feature/editor') # only need to install once
# above version of DT required for table editing

library(shiny)
library(DT)
library(XLConnect)


shinyApp(
  ui = fluidPage(
    DT::dataTableOutput('x1')
  ),
  
  server = function(input, output, session) {
    
    # QAQC Apply Column Settings
    col.ApplyQAQC <- 8
    color.ApplyQAQC <- 'yellow'
    # table caption
    myCaption <- "Double-click to edit a cell in column Apply.QAQC (highlighted in green [TRUE] or red [FALSE]).  Edits are only allowed in this column and only for the values TRUE and FALSE."
    #
    
    # load my File
    # data_QAQC <-  DT::datatable(XLConnect::readWorksheetFromFile("external/DDT_QAQC_Default.xlsx"
    #                                           , sheet="Methods Table"
    #                                           , startRow=6
    #                                           , header=TRUE
    #                                           #, drop=c(13,14)
    #                                           )
    #                             , caption=myCaption
    #                             , rownames=FALSE
    #                             , selection='none'
    #                             #, server=TRUE
    #                             # ) %>% formatStyle(columns=col.ApplyQAQC
    #                             #                   ,background=color.ApplyQAQC
    #                             #                   ,fontWeight='bold')
    #                             # Could potentially color cells based on content;
    #                             # https://rstudio.github.io/DT/010-style.html
    #                             # can't get working with column 8 and TRUE/FALSE
    #                             ) %>% formatStyle(columns=8
    #                                             , target="cell"
    #                                             , background=styleEqual(c(1,0)
    #                                                                     ,c('lightgreen','red'))
    #                                             , fontWeight='bold'
    #                                             )
    #                             # #works on column 10 (units)
    #                             # ) %>% formatStyle(columns=10
    #                             #                 , target="cell"
    #                             #                 , background=styleEqual(c("µg/L","mg/m2")
    #                             #                                         ,c('lightgreen','red'))
    #                             #                 )

     data_QAQC <-  XLConnect::readWorksheetFromFile("external/DDT_QAQC_Default.xlsx"
                                              , sheet="Methods Table"
                                              , startRow=6
                                              , header=TRUE
                                              )
    
    #x = data_QAQC
    
    # have to do formating on datatable before render.  Render has reduced options.
    
    # output$x1 = DT::renderDataTable(data_QAQC
    #                                  , server=TRUE
    #                                 #, selection = list(target="column",selected=7)
    #                                 #, rownames = FALSE
    #                                 #, caption = myCaption
    #                                 # , options = list(
    #                                             # , formatStyle(columns=8
    #                                             #             #, target="column"
    #                                             #             , background="yellow")
    #                                             # #)
    #                                 ) 
    
    output$x1 = DT::renderDataTable(DT::datatable(data_QAQC
                                                  , caption=myCaption
                                                  , rownames=FALSE
                                                  , selection='none'
                                                  ) %>% formatStyle(columns=8
                                                        , target="cell"
                                                        , background=styleEqual(c(1,0)
                                                                                ,c('lightgreen','red'))
                                                        , fontWeight='bold'
                                                        )
                                                  
      
                                    )
    

   # %>% formatStyle(8,background='yellow')
    
    #formatStyle(table="x1",columns="apply", backgroundColor='blue', fontWeight = 'bold') 
    #, searchHighlight=TRUE
    
    proxy_dt_QAQC = dataTableProxy('x1') 
    
    observeEvent(input$x1_cell_edit, {
      info = input$x1_cell_edit
      str(info)
      i = info$row
      j = info$col + 1
      v = info$value
      # Change Value "v" only IF column = 8 AND logical (T/F)
      if(j==col.ApplyQAQC & (toupper(v)=="FALSE" | toupper(v)=="TRUE")) {
      #if(j==col.ApplyQAQC) {
        data_QAQC[i, j] <<- DT:::coerceValue(toupper(v), data_QAQC[i, j])
        replaceData(proxy_dt_QAQC, data_QAQC, resetPaging = FALSE, rownames = FALSE) 
        # lose formatting of replaced table
      }
      
    })
  }
)
```

# Try 2 to mimic ddt
20170824
```{r, eval=FALSE}

library(shiny)
library(DT)
library(XLConnect)

source("external/dataQAQC.R", local=TRUE)

shinyApp(
  ui = fluidPage(
    DT::dataTableOutput('dt_QAQC')
  ),
  
  server = function(input, output, session) {
    
    
    # read_data_QAQC <- function(strFile, strSheet, intStartRow) {
    #             XLConnect::readWorksheetFromFile(strFile
    #                                              , sheet=strSheet
    #                                              , startRow=intStartRow
    #                                              , header=TRUE) #, drop=c(1,2))
    # }
    #   #data_QAQC <- XLConnect::readWorksheetFromFile("external/DDT_QAQC_Default.xlsx", sheet="Methods Table", startRow=6, header=TRUE)
    #   #
    # data_QAQC <- read_data_QAQC(strFile="external/DDT_QAQC_Default.xlsx", strSheet = "Methods Table", intStartRow=6)
    # 
    
    #data_QAQC <- XLConnect::readWorksheetFromFile("external/DDT_QAQC_Default.xlsx"
   #                                          , sheet="Methods Table", startRow=6, header=TRUE)
        
    
    ApplyQAQC.column <- 8
    data_QAQC_caption <- "Double-click to edit a cell in column Apply.QAQC (highlighted in green [TRUE] or red 
    [FALSE]).  Edits are only allowed in this column and only for the values TRUE and FALSE."
    
    output$dt_QAQC = DT::renderDataTable(DT::datatable(data_QAQC
                                                       , caption=data_QAQC_caption
                                                       , rownames=FALSE
                                                       , selection='none'
                                                      # , server=TRUE
                                                      ) %>% formatStyle(columns=ApplyQAQC.column
                                                                        ,target="cell"
                                                                        ,background=styleEqual(c(1,0)
                                                                                    ,c('lightgreen','red'))
                                                                        ,fontWeight='bold')
                                          )
    #outputOptions(output, 'dt_QAQC', suspendWhenHidden=TRUE)
    
    proxy_dt_QAQC <- DT::dataTableProxy('dt_QAQC')
    
    observeEvent(input$dt_QAQC_cell_edit, {
      info = input$dt_QAQC_cell_edit
      str(info)
      i = info$row
      j = info$col + 1
      v = info$value
      # Change Value "v" only IF column = 8 AND logical (T/F)
      if(j==8 & (toupper(v)=="FALSE" | toupper(v)=="TRUE")) {
        data_QAQC[i, j] <<- DT:::coerceValue(toupper(v), data_QAQC[i, j])
        replaceData(proxy_dt_QAQC, data_QAQC, resetPaging = FALSE, rownames = FALSE)
      }
      
      #need to update actual table (might be done with above statement)
      
    })
  
  }
)


```


# working version with Knowledge Base
20170809 email
```{r, eval=FALSE}
#devtools::install_github('rstudio/DT@feature/editor') # only need to install once

library(shiny)
library(DT)
library(XLConnect)

shinyApp(
  ui = fluidPage(
    DT::dataTableOutput('x1')
  ),
  server = function(input, output, session) {
    
    # load my File
    data_QAQC <- XLConnect::readWorksheetFromFile("external/DDT_QAQC_Default.xlsx"
                                              , sheet="Methods Table", startRow=6, header=TRUE)
    
    #x = data_QAQC
    myCaption <- "Double-click to edit a cell.  'TRUE' and 'FALSE' are the only values allowed.  And only for column 'apply'."

    output$x1 = DT::renderDataTable(data_QAQC, server=TRUE, selection = 'none', rownames = FALSE
                                    , caption = myCaption)
    
    #formatStyle(table="x1",columns="apply", backgroundColor='blue', fontWeight = 'bold') 
    
    proxy_dt_QAQC = dataTableProxy('x1')
    
    observeEvent(input$x1_cell_edit, {
      info = input$x1_cell_edit
      str(info)
      i = info$row
      j = info$col + 1
      v = info$value
      # Change Value "v" only IF column = 8 AND logical (T/F)
      if(j==8 & (toupper(v)=="FALSE" | toupper(v)=="TRUE")) {
        data_QAQC[i, j] <<- DT:::coerceValue(toupper(v), data_QAQC[i, j])
        replaceData(proxy_dt_QAQC, data_QAQC, resetPaging = FALSE, rownames = FALSE)
      }
      
    })
  }
)
```


