---
title: "NEWS; Data Discovery Tool QAQC Updates"
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

Version history.

# Planned Updates

* Entered issues on GitHub for remaining planned updates.
https://github.com/tetratech/DataDiscoveryTool/issues

# v1.1.0.9003
2017-07-26

* Added additional filters on the View Data page.  Issue #5.

* Completed save/load queries.  Issue #2.

* Added buttons to save/load filters.  (not complete).  Issue #4.

* Added button to save data on Check Data.  (not complete). Issue #7

# v1.1.0.9002
2017-07-18

* Added ability to save and load queries.  (not complete).  Issue #2.  20170718.

# v1.1.0.9001
2017-07-11

* Added NEWS and README.

* Added RStudio project file.

* Added Notebook for tracking items with the update.

# v1.1.0.9000
2017-07-11

* Created GitHub repository.  2017-06-16.

* Pulled /app/tool/ files from v1.1 of the ddt into stand alone folder.

* Uses R v3.3.1.
