---
title: "Data Discovery Tool, Packages"
output: html_notebook
---
2017-09-21

The Data Discovery Tool (ddt) created by USEPA for use with Water Quality Data Portal (v1.1.0.0000).

# Packages
A number of packages are included with the ddt and ship in the R portal version.

In order run as a stand alone version the user will need the to install multiple packages as noted in the R code below.

The only "new" package added for the QAQC work by Tetra Tech is "XLConnect".
```{r, eval=FALSE}
# libraries to be installed
data.packages = c("assertthat"
                  , "base64enc"
                  , "chron"
                  , "data.table"
                  , "dataRetrieval"
                  , "DBI"
                  , "devtools"
                  , "dplyr"
                  , "DT"
                  , "ggplot2"
                  , "git2r"
                  , "htmlwidgets"
                  , "httpuv"
                  , "httr"
                  , "jsonlite"
                  , "lazyeval"
                  , "leaflet"
                  , "lubridate"
                  , "memoise"
                  , "openssl"
                  , "png"
                  , "R6"
                  , "raster"
                  #, "rCharts" #non-CRANN
                  , "readr"
                  , "rstudioapi"
                  , "scales"
                  , "shiny"
                  , "shinyBS"
                  , "sourcetools"
                  , "sp"
                  , "stringr"
                  , "tibble"
                  , "whisker"
                  , "withr"
                  , "xml2"
                  , "xtable"
                  , "XLConnect"
                  )
# install via lapply
lapply(data.packages,function(x) install.packages(x))
```

One package, rCharts, is a non-CRAN package and needs to be installed separately.

A second package, DT, requires a specific version that is not hosted on CRAN.  This specific version of DT was used in edits to the ddt to enable on screen editing for the QAQC Decisions table.  This version of DT will need to be installed from GitHub with the code below.
```{r, eval=FALSE}
# Install non-CRAN packages from GitHub
require(devtools)
install_github("ramnathv/rCharts")
install_github('rstudio/DT@feature/editor')
```

If after running the ddt the user is presented with an error message about not having a package then the user should reinstall that specific package.  Replace "XLConnect" in the code below with the name of the missing package.
```{r, eval=FALSE}
# libraries to be installed
data.packages = c("XLConnect")
# install via lapply
lapply(data.packages,function(x) install.packages(x))
```
